Implicit Neural Representation for Potential Field Geophysics

### 2023-10-12 discussion.tex
Update comparison figure

\section[Super-resolution for domain specific tasks]{A structured approach to training super-resolution for domain specific tasks}
Several models were implemented throughout \Cref{ch:paper1,ch:paper2}, namely RDN\textdaggerdbl{}, ESRGAN+, and LTE\@.
% However, the most important choice in developing a performant super-resolution neural network for real-world aeromagnetic survey data was the choice of training data.
The work in \Cref{ch:paper1} was prepared for publication prior the release of a large and varied synthetic geology training dataset \parencite{jessellNoddyverseMassiveData2022}.
It was seen in \Cref{ch:paper2} that this data improved model performance for a range of features by using transfer learning for pre-training.
% This transfer learning approach for training data is also found to be useful for RDN\textdaggerdbl{} and ESRGAN\@.
Here, the use of synthetic and real-world line spacing sampled data approach used with LTE in \Cref{ch:paper2} are adopted for the RDN\textdaggerdbl{} and ESRGAN+ models.
\Cref{fig:modcomp} shows RDN\textdaggerdbl{} and ESRGAN+ in predicting accurate features when upscaling \qty{320}{\m} data to \qty{80}{\m} line spacing.
It can be inferred that the challenge of super-resolution for these tasks is predominantly a question of providing suitable and sufficient training data, and is less constrained to neural network choices.

\begin{figure}
    \includegraphics[width=\linewidth]{fig/etc/TMI Comparison_23.pdf} % TODO Update for RDN\textdaggerdbl{}, ESRGAN, LTE, ~3 hours ea.
    \caption[Comparison between the three SR architectures]{
        A comparison between all deep learning super-resolution methods presented in \Cref{ch:paper1} and \Cref{ch:paper2}, using the realistic low-resolution transform developed in \Cref{ch:paper2}.
        a) The low-resolution input, b) The high-resolution target, c) The RDN\textdaggerdbl{}+ Network, d) The ESRGAN+ network, and e) The LTE network.}
    \label{fig:modcomp}
\end{figure}

>>>>

\section[Super-resolution for domain specific tasks]{A structured approach to training super-resolution for domain specific tasks}
Several models were implemented throughout \Cref{ch:paper1,ch:paper2}, namely RDN\textdaggerdbl{}, ESRGAN+, and LTE\@.
% However, the most important choice in developing a performant super-resolution neural network for real-world aeromagnetic survey data was the choice of training data.
The work in \Cref{ch:paper1} was prepared for publication prior the release of a large and varied synthetic geology training dataset \parencite{jessellNoddyverseMassiveData2022}.
It was seen in \Cref{ch:paper2} that this data improved model performance for a range of features by using transfer learning for pre-training.
% This transfer learning approach for training data is also found to be useful for RDN\textdaggerdbl{} and ESRGAN\@.
Here, the use of synthetic and real-world line spacing sampled data approach used with LTE in \Cref{ch:paper2} are adopted for the RDN\textdaggerdbl{} and ESRGAN+ models.
\Cref{fig:modcomp} shows RDN\textdaggerdbl{}, ESRGAN+, and LTE predicting accurate structural features when upscaling \qty{320}{\m} data to \qty{80}{\m} line spacing.
While each model has different hyperparameters due to the different architectures in use, the SR prediction converges toward similar structures, with ESRGAN+ containing additional noise.
It can be interpreted that the challenge of super-resolution for this tasks is predominantly a question of providing suitable and sufficient training data, and is less constrained to neural network choices.

\begin{landscape}
    \begin{figure}[hbtp]
        \includegraphics[width=\linewidth,trim={0 0 0 5mm},clip]{fig/etc/model_comparison_v2.pdf}
        \caption[Comparison between the three SR architectures]{
            A comparison between all deep learning super-resolution methods presented in \Cref{ch:paper1} and \Cref{ch:paper2}, using the realistic low-resolution transform developed in \Cref{ch:paper2}.
            a) The low-resolution input, b) The high-resolution target, c) The RDN\textdaggerdbl{} SR prediction, d) The ESRGAN+ SR prediction, and e) The LTE SR prediction.}
        The baseline model for c) and d) was trained for 7 hours on the synthetic dataset described in \Cref{sec:2methods}.
        c) was fine-tuned for 1.5 hours, while d) was fine-tuned for 4.3 hours.
        The training of e) is described in \Cref{sec:finetune}.
        \label{fig:modcomp}
    \end{figure}
\end{landscape}
